\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/discussion.tex
rearranged discussion.

\subsection{Resilience of \speculake}
%Spectre works to use a cache side-channel to leak information from a process. As
%such defenses to Spectre work to limit the information available to a
%speculatively executing program. 
%
\subsubsection{Spectre Versions}
In this work we have implemented applications making use of the speculative
primitive in Spectre version 2, however the speculative primitive is not 
unique to this varaint. The \speculake model can be applied more broadly
across the spectrum of speculative functionality to hide malicious computation.

For example an attacker could construct a series of direct branches with 
contradictory conditions such that the resulting code section can never 
be on a real world execution path. This, however does not prevent such a path
from occuring speculatively. An attacker could use such an impossible path to
hide speculative logic that influences the malware, effectively obscuring the
speculative entry point.
Similarly, the speculative store bypass variant~\cite{spec-store-bypass} could be used to
redirect control flow when the mis-speculated load is that of an indirect
branch target or function pointer.

% we demonstrated this, hopefully
%Alternatively, recent variants of Spectre version 1 could be used to
%redirect control flow in speculative overflow style attacks~\cite{kiriansky2018speculative}. 
%Using this technique speculative gadgets could be executed
%based on attacker controlled input.

%Again the speculative primitive could 
%be employed to execute speculative gadgets.

%These alternatives create an even larger attack area for a potential 
%reverse engineer as the attacker can pivot between them with minimal alterations.

\if0
%Cutting this for now. We sort of cover it in the Turing section(s)
\subsubsection{Gadget Location}
The benefits of \speculake rely on the computation performed in the
speculative world being well hidden. To this end we have verified 
certain requirements about the locations that a speculative gadget can 
be placed within a binary.

@@

\subsubsection{Hypervisors}
For virtual environments that provide guests significant periods of access to
hardware resources, \speculake is viable in certain configurations. 
This result is specific to Spectre 2 variant, as it relies on 
the indirect branch predictor effecting the branches in either the host 
or guest environment. We have found that the hypercall context switch from 
guest to host is light enough that a trigger program running in a guest
can effect the branch predictor in a host on the same CPU core. This is not
true in the opposite direction (where the trigger runs on the host) as the 
hypercall transition seems to be more substantial. This implies, and we have verified,
that guest-to-guest indirect branch predictor interference, and the current
\speculake implementation, will not work across disparate virtual environments.

@@

>>>>

\if0
%Cutting this for now. We sort of cover it in the Turing section(s)

\subsection{Resilience of \speculake}
%Spectre works to use a cache side-channel to leak information from a process. As
%such defenses to Spectre work to limit the information available to a
%speculatively executing program.

\subsubsection{Gadget Location}
The benefits of \speculake rely on the computation performed in the
speculative world being well hidden. To this end we have verified 
certain requirements about the locations that a speculative gadget can 
be placed within a binary.

@@

@@

\subsubsection{Hypervisors}
For virtual environments that provide guests significant periods of access to
hardware resources, \speculake is viable in certain configurations. 
This result is specific to Spectre 2 variant, as it relies on 
the indirect branch predictor effecting the branches in either the host 
or guest environment. We have found that the hypercall context switch from 
guest to host is light enough that a trigger program running in a guest
can effect the branch predictor in a host on the same CPU core. This is not
true in the opposite direction (where the trigger runs on the host) as the 
hypercall transition seems to be more substantial. While this implies 
that guest-to-guest indirect branch predictor interference, and the current
\speculake implementation, will not work across disparate virtual environments,
strict resource isolation gives a stronger guarantee of non-interference.
